Comparing Early Evolution of Flames in X-ray Bursts in Two and Three Dimensions

### 2023-03-15 xrb3/paper.tex
A pair of edits to first paragraph

X-ray bursts (XRBs) result from thermonuclear burning of an accreted
H/He or He layer on a neutron star \citep{galloway:2017}.
Observations of brightness oscillations in the rise of the lightcurve
suggest that the burning begins localized and then spreads across the
neutron star \citep{bhattacharyya:2007}. 
This spreading is inherently
a multi-dimensional phenomenon, requiring hydrodynamic simulations that
resolve the reactive zone, realistic reaction networks, and
domain sizes that capture the scales over which rotation in order to
understand the flame propagation and nucleosynthesis.  Detailed
nuclear physics is especially important for understanding the 
rp-process in mixed H/He bursts, as discussed in \citealt{rpprocess}.

>>>>

X-ray bursts (XRBs) result from thermonuclear burning of an accreted
H/He or He layer on a neutron star \citep{galloway:2017}.
Observations of brightness oscillations in the rise of the lightcurve
suggest that the burning begins localized and then spreads across the
neutron star \citep{bhattacharyya:2007}. 
This spreading is inherently
a multi-dimensional phenomenon, requiring hydrodynamic simulations that
resolve the reactive zone, realistic reaction networks, and
domain sizes that capture the scales over which rotation is important in order to
understand the flame propagation and nucleosynthesis.  Detailed
nuclear physics is especially important for understanding the 
rp-process in mixed H/He bursts, as discussed in \citet{rpprocess}.
